---
title: "Untitled"
author: "Ritesh Kumar Malaiya"
date: "Thursday, August 06, 2015"
output: 
  html_document: 
    toc: yes
---


# Load Required libraries
```{r}
if(!require(dplyr)) {
  install.packages('dplyr')
  suppressPackageStartupMessages(require(dplyr))
}

if(!require(plyr)) {
  install.packages('plyr')
  suppressPackageStartupMessages(require(plyr))
}

if(!require(arules)) {
  install.packages('arules')
  suppressPackageStartupMessages(require(arules))
}

if(!require(arulesViz)) {
  install.packages('arulesViz')
  suppressPackageStartupMessages(require(arulesViz))
}

```

# Data Processing
## Load Data
```{r}
teamdata <- read.csv("teamdata.csv")
size <- 1:nrow(teamdata)
```

## Convert Data to Event\Itemsets Format
```{r}
teamdata$seconds <- sample(x =  1:(4*60),size = nrow(teamdata), replace = T)

teamdata.event <- teamdata %>% ddply( ~ project ~ name ~ date ~ seconds, function(x) {
                                      ddply(x, ~seconds, function(y) {
    
                                        data.frame(email = as.character(ifelse (y$email_count == 0, NA, paste0(y$email_count,"EMAIL",length(unique(y$name))))),
                                                   svn = as.character(ifelse (y$svn_count == 0, NA, paste0(y$svn_count,"SVN",length(unique(y$name))))),
                                                   watches = as.character(ifelse (y$watches == 0, NA, paste0(y$watches,"WATCHES",length(unique(y$name))))),
                                                   votes = as.character(ifelse (y$votes == 0, NA, paste0(y$votes,"VOTES",length(unique(y$name))))),
                                                   jira_count = as.character(ifelse (y$jira_count == 0, NA, paste0(y$jira_count,"JIRA_COUNT",length(unique(y$name))))),
                                                   jira_type = as.character(ifelse (y$jira_type == 0, NA, paste0(y$jira_type,"JIRA_TYPE",length(unique(y$name))))),
                                                   jira_priority = as.character(ifelse (y$jira_priority == 0, NA, paste0(y$jira_priority,"JIRA_PRIORITY",length(unique(y$name)))))
                                                   )
      })
}
)

teamdata.event <- teamdata %>% ddply( ~ project ~ name ~ date ~ seconds, function(x) {
                                      ddply(x, ~seconds, function(y) {
    
                                        data.frame(email = ifelse (y$email_count == 0, '1EMAIL1', paste0(y$email_count,"EMAIL",length(unique(y$name)))),
                                                   svn = ifelse (y$svn_count == 0, '1SVN1', paste0(y$svn_count,"SVN",length(unique(y$name)))),
                                                   watches = ifelse (y$watches == 0, '1WATCHES1', paste0(y$watches,"WATCHES",length(unique(y$name)))),
                                                   votes = ifelse (y$votes == 0, '1VOTES1', paste0(y$votes,"VOTES",length(unique(y$name)))),
                                                   jira_count = ifelse (y$jira_count == 0, '1JIRA_COUNT1', paste0(y$jira_count,"JIRA_COUNT",length(unique(y$name)))),
                                                   jira_type = ifelse (y$jira_type == 0, '1JIRA_TYPE1', paste0(y$jira_type,"JIRA_TYPE",length(unique(y$name)))),
                                                   jira_priority = ifelse (y$jira_priority == 0, '1JIRA_PRIORITY1', paste0(y$jira_priority,"JIRA_PRIORITY",length(unique(y$name))))
                                                   )
      })
}
)
str(teamdata.event)
head(teamdata.event)

```


## Quality of Data

1. Total size of Data
```{r}
dim(teamdata.event)
```

2. Total rows not having any missing events
```{r}
sum(complete.cases(teamdata.event))
```

3. Total cells/instances having any missing events
```{r}
sum(is.na(teamdata.event))
```

As we can see that the data is in good condition, let's proceed with applying Apriori Algorithm

```{r}
write.csv(teamdata.event, file = "fp_growth.csv", na = "")

```

## Association Rule Mining using Apriori

### Finding rules:

With Support 0.2 and Confidence 80%
```{r}

rules.all <- apriori(teamdata.event[,-(1:4)], control = list(verbose=T), parameter = list(minlen=5, supp = 0.2, conf=0.8))

quality(rules.all) <- round(quality(rules.all), digits=3)
inspect(rules.all)

rules.sorted <- sort(rules.all, by = 'lift')
inspect(rules.sorted)
```

### Plotting Association Rules

```{r}

#png("FPGrowth1.png", width = 1390, height = 732)
plot(rules.all)
#dev.off()

#png("FPGrowth2.png", width = 1390, height = 732)
plot(rules.all, method = "grouped")
#dev.off()

#png("FPGrowth3.png", width = 1390, height = 732)
plot(rules.all, method = "graph")
#dev.off()

#png("FPGrowth4.png", width = 1390, height = 732)
plot(rules.all, method = "graph", control = list(type = 'items'))
#dev.off()

#png("FPGrowth5.png", width = 1390, height = 732)
plot(rules.all, method = "paracoord", control = list(reorder = TRUE))
#dev.off()
